Inference methods comparison for the simplified Naomi model

### 2023-04-27 src/naomi-simple_compare/comparison.Rmd
Two small errors
Check issue with KS == 1 -- related to specific age groups (infants and >80) #30

@@

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper <- function(par) lapply(1:sum(names(tmb$fit$obj$env$par) == par), histogram_and_ecdf, par = par)
histogram_and_ecdf_helper("beta_rho")
```

@@

ks_plot(ks_df = ks_rho_t1_out, par = "rho_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_alpha_t1_out, par = "alpha_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_lambda_t1_out, par = "lambda_t1_out", alpha = 0.2)
```

>>>>

```{r}
histogram_and_ecdf_helper <- function(par) lapply(1:sum(names(tmb$fit$obj$env$par) == par), histogram_and_ecdf, par = par)
```

@@

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("beta_rho")
```

@@

ks_plot(ks_df = ks_rho_t1_out, par = "rho_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_alpha_t1_out, par = "alpha_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_lambda_t1_out %>% filter(!(age_group %in% c("Y005_009", "Y010_014", "Y080_999"))), par = "lambda_t1_out", alpha = 0.2)
```

What is going on with those very high values of KS?

```{r}
ks_lambda_t1_out %>%
  filter(ks > 0.99) %>%
  group_by(method) %>%
  summarise(n = n())

ks_lambda_t1_out %>%
  filter(ks > 0.99) %>%
  pull(age_group) %>%
  unique()
```
